---
output: github_document
editor_options: 
  chunk_output_type: console
html_document:
  df_print: paged
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# catalogoUCsBR

<!-- badges: start -->

[![R-CMD-check](https://github.com/p/catalogoUCsBR/pablopains/R-CMD-check/badge.svg)](https://github.com/pablopains/catalogoUCsBR/actions) [![Codecov test coverage](https://codecov.io/gh/pablopains/catalogoUCsBR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/pablopains/catalogoUCsBR?branch=main) [![R-CMD-check](https://github.com/pablopains/catalogoUCsBR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/pablopains/catalogoUCsBR/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->
The **catalogoUCsBR** package is designed to convert species occurrence data from the Jabot Geral, Jabot RB, Reflora, SpeciesLink and GBIF data portals into a more understandable format for use in preparing species listings for the [Plant Catalog of Units of Brazilian Conservation](https://catalogo-ucs-brasil.jbrj.gov.br/).

## Installation

You can install the development version of catalogoUCsBR from [GitHub](https://github.com/pablopains/catalogoUCsBR).
To install catalogoUCsBR, run 

```{r example_install, eval=FALSE}
devtools::install_github("pablopains/catalogoUCsBR")
```


## **Use the online application in: [pablopains.shinyapps.io/catalogoUCsBR/](https://pablopains.shinyapps.io/catalogoUCsBR/)**


## **Workflow performed in just a few clicks using the application locally**
We recommend using the application locally.
```{r example_app, eval=FALSE}
catalogoUCsBR::load_app()
```


## **Consult the [catalogoUCsBR Manual](https://github.com/pablopains/catalogoUCsBR/blob/main/catalogoUCsBR_1.0.0.pdf) for a case study with a complete and replicable workflow**

Please site catalogoUCsBR as:
```{r example_citation, eval=TRUE}
print(citation("catalogoUCsBR"), bibtex = FALSE)
```


