---
output: github_document
editor_options: 
  chunk_output_type: console
html_document:
  df_print: paged
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# catalogoUCsBR

<!-- badges: start -->

[![R-CMD-check](https://github.com/p/catalogoUCsBR/pablopains/R-CMD-check/badge.svg)](https://github.com/pablopains/catalogoUCsBR/actions) [![Codecov test coverage](https://codecov.io/gh/pablopains/catalogoUCsBR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/pablopains/catalogoUCsBR?branch=main) [![R-CMD-check](https://github.com/pablopains/catalogoUCsBR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/pablopains/catalogoUCsBR/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->
The **catalogoUCsBR** package is designed to convert herbarium species occurrence data from JABOT, Reflora, speciesLink, and GBIF data portals into a suitable format to prepare plant species lists revised for the [Catalog of Plants of Conservation Units in Brazil](https://catalogo-ucs-brasil.jbrj.gov.br/). The package provides tools to verify and standardize scientific names of species, join duplicates, and select species records as a voucher to compose lists of plant species in UCs in Brazil, helping to understand and protect the biodiversity in protected areas.



## Installation

You can install the development version of catalogoUCsBR from [GitHub](https://github.com/pablopains/catalogoUCsBR).
To install catalogoUCsBR, run 

```{r example_install, eval=FALSE}
install.packages('remotes',  dependencies = T)

remotes::install_github("pablopains/catalogoUCsBR",
                        dependencies = T)
```

# **Botanical experts**

## **Use the prepare app locally in RStudio**
```{r example_app_prepare, eval=FALSE}
catalogoUCsBR::app_prepare()
```

## **Use the review app locally in RStudio**
```{r example_app_review, eval=FALSE}
catalogoUCsBR::app_review()
```

## **Consult the [catalogoUCsBR Manual](https://github.com/pablopains/catalogoUCsBR/blob/main/catalogoUCsBR_1.0.4.pdf) for a case study with a complete and replicable workflow**

Please site catalogoUCsBR as:
```{r example_citation, eval=TRUE}
print(citation("catalogoUCsBR"), bibtex = FALSE)
```


